Gsmodutils: A python based framework for test driven genome scale metabolic model development

### 2018-09-24 article/article.tex
Article changes

\author{James P Gilbert}
\email{james.gilbert@nottingham.ac.uk}
\author{Nicole Pearcy}
\author{Rupert Norman}
\affiliation[sbrc]{Synthetic Biology Research Centre, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}
\author{Jamie Twycross}
\affiliation[IMA]{Intelligent Modelling and Analysis group, School of Computer Science, University of Nottingham, Nottingham, NG8 1BB, United Kingdom}
\author{John King}
\affiliation[Maths]{School of Mathematical Sciences, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}
\author{Charlie Hodgman}
\affiliation[Biosciences]{School of Biosciences, University of Nottingham, Sutton Bonington, Loughborough, LE12 5RD, United Kingdom}
\author{Nigel Minton}
\affiliation[sbrc]{Synthetic Biology Research Centre, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}

@@

\begin{acknowledgement}
We would like to thank the Oxford Brookes Cell Systems Modelling group for helpful discussions regarding this work and Thomas Millat for scientific advice.
This work was supported by the UK Biotechnology and Biological Sciences Research Council (BBSRC) grants BB/L013940/1,  BB/K00283X/1 and BB/L502030/1.
\end{acknowledgement}

>>>>

\author{James P Gilbert}
\email{james.gilbert@nottingham.ac.uk}
\author{Nicole Pearcy}
\author{Rupert Norman}
\affiliation[sbrc]{Synthetic Biology Research Centre, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}
\author{Thomas Millat}
\affiliation[sbrc]{Synthetic Biology Research Centre, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}
\author{Klaus Winzer}
\affiliation[sbrc]{Synthetic Biology Research Centre, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}
\author{John King}
\affiliation[Maths]{School of Mathematical Sciences, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}
\author{Charlie Hodgman}
\affiliation[Biosciences]{School of Biosciences, University of Nottingham, Sutton Bonington, Loughborough, LE12 5RD, United Kingdom}
\author{Nigel Minton}
\affiliation[sbrc]{Synthetic Biology Research Centre, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}
\author{Jamie Twycross}
\affiliation[IMA]{Intelligent Modelling and Analysis group, School of Computer Science, University of Nottingham, Nottingham, NG8 1BB, United Kingdom}

@@

\begin{acknowledgement}
We would like to thank the Oxford Brookes Cell Systems Modelling group for helpful discussions regarding this work and for scientific advice.
This work was supported by the UK Biotechnology and Biological Sciences Research Council (BBSRC) grants BB/L013940/1,  BB/K00283X/1 and BB/L502030/1.
\end{acknowledgement}
